---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stocksignalsr

<!-- badges: start -->
<!-- badges: end -->

The goal of stocksignalsr is to be used as a starting point for identifying stock buy/sell signals. Stock investing is a complex process which requires ongoing efforts and there is no one formula or indicator that works all the time. There exists extensive research on how to identify opportunities and profit from stocks. Methodologies for evaluating financial instruments range widely. An investor can utilize macroeconomic research, fundamental analysis, news, analyst reports, or technical analysis. In all those approaches numerical analysis is the underlying common theme.

In this project, the team aims to evaluate three key technical indicators that can be used to evaluate where the stock price is relative to its historic performance. These indicators use only the stock's historic price and are by no means an exhaustive approach to investing. These indicators are:

200-day price moving average
10 vs 20-day price moving average
20-day Bollinger bands
Typically when the market and stocks in particular are trading below 200-day moving average, they are considered in a down trend. When they trade above the 200-day moving average stocks are considered in an uptrend. The 10-20 day indicator, indicates short term price trend reversals, and can be utilized to trade stocks on a short term basis. Finally, the Bollinger bands indicate whether a stock price is above or below two standard deviations from its 20 day average price. Bbands can be used as indicator for short term overbought/oversold stocks.


## Package details
Package details
The package consists of 6 functions:

* get_data: The function downloads all available historic price data for a selected stock and saves it. It utilizes the yfinance python package to automate the process.
* moving_average: The function (inside calc_moving_average.py module) calculates a moving average, i.e. the average stock closing price over a specified period, which is passed as argument size in the function call. It uses the data saved via get_data.
* plot_ma_200days: The function plots the 200-day moving average together with the stock price for a specified period, say the past 200 trading days. It uses the output from the function calc_moving_avg to plot the chart.
* plot_ma_10_20: The function plots the 10 and 20-day moving average together with the stock price for a specified period, say the past 200 trading days. It uses the output from function move_ave_10_20 to plot the chart.
* get_bbands: The function (inside bbands.py module) calculates the 20 day Bollinger bands for the existing period of the data and returns a Pandas DataFrame with the respective upper and lower band. It uses data saved via get_data.
* plot_bbands: The function plots upper and lower Bollinger bands together with the stock closing price for over the past 200 days. It uses the output from function bbands to plot the chart.

## R ecosystem

There are multiple packages related to utilizing finance data. For example, past projects in DSCI524 have explored various transformations to help analyzing stocks like this one: https://github.com/UBC-MDS/stockAnalyzer.

Our aim is to explore specific technical analysis indicators and streamline the process by providing a hands-on package which can be used in daily stock analysis. Furthermore, this package will help streamline the process in order to help automation of the basics of stock screening.



## Installation

You can install the development version of stocksignalsr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("UBC-MDS/stocksignalsr")
```




## Usage


```{r example}
library(stocksignalsr)
```


