---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# stocksignalsr

<!-- badges: start -->
<!-- badges: end -->

The goal of stocksignalsr is to be used as a starting point for identifying stock buy/sell signals. Stock investing is a complex process which requires ongoing efforts and there is no one formula or indicator that works all the time. There exists extensive research on how to identify opportunities and profit from stocks. Methodologies for evaluating financial instruments range widely. An investor can utilize macroeconomic research, fundamental analysis, news, analyst reports, or technical analysis. In all those approaches numerical analysis is the underlying common theme.


## Installation

You can install the development version of stocksignalsr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("UBC-MDS/stocksignalsr")
```

## Usage


```{r example}
library(stocksignalsr)


```


