---
title: "Package usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction
The goal of stocksignalsr is to be used as a starting point for
identifying stock buy/sell signals. Stock investing is a complex process
which requires ongoing efforts and there is no one formula or indicator
that works all the time. There exists extensive research on how to
identify opportunities and profit from stocks. Methodologies for
evaluating financial instruments range widely. An investor can utilize
macroeconomic research, fundamental analysis, news, analyst reports, or
technical analysis. In all those approaches numerical analysis is the
underlying common theme.

In this project, the team aims to evaluate three key technical
indicators that can be used to evaluate where the stock price is
relative to its historic performance. These indicators use only the
stock’s historic price and are by no means an exhaustive approach to
investing. These indicators are:

200-day price moving average 10 vs 20-day price moving average 20-day
Bollinger bands. Typically when the market and stocks in particular are
trading below 200-day moving average, they are considered in a down
trend. When they trade above the 200-day moving average stocks are
considered in an uptrend. The 10-20 day indicator, indicates short term
price trend reversals, and can be utilized to trade stocks on a short
term basis. Finally, the Bollinger bands indicate whether a stock price
is above or below two standard deviations from its 20 day moving average price.
Bbands can be used as indicator for short term overbought/oversold
stocks.

## Package details

The package consists of 6 functions:

-   `get_data`: The function downloads all available historic price data
    for a selected stock and saves it. It utilizes the tidyquant R
    package to automate the process.
-   `moving_average`: The function calculates a moving average, i.e.the
    average stock closing price over a specified period, which is passed
    as argument size in the function call. It uses the data saved via
    get_data.
-   `plot_ma_200days`: The function plots the 200-day moving average
    together with the stock price for a specified period. It uses the
    output from the function moving_average to plot the chart.
-   `plot_ma_10_20`: The function plots the 10 and 20-day moving average
    together with the stock price for a specified period. It uses the
    output from function moving_average to plot the chart.
-   `get_bbands`: The function calculates the 20 day Bollinger bands for
    the existing period of the data and returns a dataframe with the
    respective upper and lower band. It uses data saved via get_data.
-   `plot_bbands`: The function plots upper and lower Bollinger bands
    together with the stock closing price for over the past 252 trading
    days. It uses the output from function get_bbands to plot the chart.


## Usage

This vignette serves the purpose of introducing the user to the package usage by demonstrating:

* Installation steps
* Example usage of functions

## Installation

The first step is installing the package:

```{r eval=FALSE}
devtools::install_github("UBC-MDS/stocksignalsr")

```


## Load package

Next, here is how to load and use the package


```{r eval=FALSE}
library(stocksignalsr)

```

## Usage

Functions can be run as demonstrated below. The example is given with Microsoft's stock price, however, any publicly traded company can be used as long as the stock ticker is entered correctly.  In order to obtain the data for each respective stock, a starting date must be entered in the form `YYYY-MM-DD`.


```{r, eval=FALSE}
get_data("MSFT", "1986-03-13")
get_bbands("MSFT")
plot_bbands("MSFT")
plot_ma_10_20days("MSFT")
moving_average("MSFT", 20)
plot_200ma("MSFT")
```















